\documentclass[]{article}

\title{Movie Reviews}
\author{Abhinav Sharma}
\author{MAdhukant}
\date

\begin{document}

\maketitle
\section{Swades Review}
5 January 2005 | by Ajit Mahadevan (India) – See all my reviews

Ashutosh Gowariker, has really made this movie straight from the heart. It has none of the ridiculous clichés one is typically used to seeing when one sees a story about an India returning home. He has captured something which perhaps no other Indian movie has - that love for ones country can be strong without making an excessively big deal about it.

It is a long movie. But I think the rather leisurely pace of the movie is required because it gives enough time for the protagonist, Mohan Bhargava, to come to India (with his mineral water and caravan) and start to fall in love with its beauty as well as understand its incongruities which frustrate us all as well. I thought there were three moments in the movie that captured it all

1. The feeling he gets when he starts to land in India. All of us feel it. I do even today. It's called coming home. 2. The mineral water - that is a classic. In fact it is a character of its own throughout the movie and plays its own part! 2. The boy serving water at 25paise to the train passengers and Mohan Bhargava's reaction

I am saddened that Indians both in India and around the world have not liked this movie. It will be remembered as an epic. 2.

\section{Chak De India}
Finally Bollywood has a full fledged sports movie.This one is certainly worth a watch for every movie lover.This is a very well made movie with nothing unnecessary being added.


Being an SRK fan I love to see him in all sorts of roles but these are the ones which bring the real actor out of him, Swades being another example.

Role of a coach is perfectly portrayed by SRK.He is the most energetic actor around and he has put it all into it.The story of this movie moves very subtly and augments the excitement every next second.

For a country like India with its national game as hockey this movie was long due.Finally, when it has arrived,it hasn't disappointed.It has also indirectly displayed the crippled Indian sports system which needs much improvement.Lets hope concerned people learn something from it.This movie can really do wonders for the next generation of aspiring hockey players.

CDI is entertaining,insightful,inspiring and yet very simple which is its greatness.This movie succeeds in bringing out tears and giggles and also lets the adrenaline flow in full pace.

The cinematography and editing are equally good.They succeeded in capturing each moment with its complete emotion.

The director has treated the subject extremely well and has brought 100 percent from all the new actors.
In last moview was very good.
\end{document}
